Curve Average \\ {\large Project 3 for CS 6491: Computer Graphics}

### 2015-11-02 paper/paper.tex
fixed some typos and doing some layout improvements

\section{Objective}
Formally, for two curves $A$ and $B$ defined by the control points $\{A_0 ... A_{n-1}\}$ and $\{B_0 ... B_{n-1}\}$, all points are in $\mathbb{R}^3$, and an interpolation scheme,
the goal is to find a curve $C$ such that for each point $c \in C$, and its closest projections
\begin{align}
a^c &= \operatornamewithlimits{argmin}\limits_{a \in A} ||a-c|| \text{, and} \\
b^c &= \operatornamewithlimits{argmin}\limits_{b \in B} ||b-c||
\end{align}

@@

\section{Input}
For simplicity, we only focus on a special case that each control curve is defined by six control points $A_0$ to $A_5$ and $B_0$ to $B_5$, such that the first and the last control points are the same.

@@

Once all the roots of the perpendicularity constraint is found, the ones with imaginary coefficients
and the ones with real values that are out of the [0,1] bound need to be eliminated. Moreover, to
choose the closest perpendicular point, an iterative comparison has to be executed as shown in 
Algorithm 1 for a quintic function. Note that the coefficients for the polynomial are obtained
through Matlab's symbolic toolbox.

\SetArgSty{textup}
\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{P_0, T_0, P_1, T_1\}$: control points, $Q$: input point}
  \KwResult{$t$: time in $[0,1]$ for the closest point}
  $[a,b,c,d,e,f] \leftarrow $generateDistanceCoeffs$(P_0,T_0,P_1,T_1,Q)$; \\
  $res \leftarrow $solveQuintic($a,b,c,d,e,f$); \\
  $\{minDist, t^*\} \leftarrow \{\infty,-1\}$;\\
  \ForEach{$r \in res$} {
    \lIf{$|r.im| > 0$} \textbf{continue}; \\
    \lIf{$r.re < 0\;$ \textbf{or} $\;r.re > 1$} \textbf{continue}; \\
    $P_t \leftarrow \tau(P_0,T_0,P_1,T_1,r.re)$; \\
    \If{$|P_t - Q| < minDist$} {
      $\{minDist, t^*\} \leftarrow \{|P_t - Q|, r.re\}$;\\
    }
  }
  \Return{$t^*$};
  \caption{closestPointOnCubicHermite()}
\end{algorithm}

@@

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves}
  \KwResult{$\mathbf{C}$: average curve}
  $\mathbf{C}.$add($\mathbf{A}[0], 0$); \\
  $\{current, t_a, t_b, t_a^\prime, t_b^\prime\} \leftarrow \{\mathbf{C}[0],0,0,0,0\}$; \\
  \While{true} {
  $\vec{T}_A \leftarrow \vec{n}$($\mathbf{A}.\tau$($min(1,t_a+\epsilon)$) - $\mathbf{A}.\tau$($min(1,t_a)$)); \\
  $\vec{T}_B \leftarrow \vec{n}$($\mathbf{B}.\tau$($min(1,t_b+\epsilon)$) - $\mathbf{B}.\tau$($min(1,t_b)$)); \\
  $current \stackrel{+}\leftarrow \text{STEP\_SIZE} \;\vec{n}(\vec{T}_A + \vec{T}_B)$; \\
  $\{t_a^\prime, t_b^\prime, r, P_c\} \leftarrow \text{snap}(\mathbf{A},\mathbf{B},current)$; \\
  \lIf{$max(t_a,t_b) < 1$ \textbf{or} $t_a^\prime < t_a$ \textbf{or} $t_b^\prime < t_b$} \textbf{break}; \\
  $\{t_a, t_b\} \leftarrow \{t_a^\prime, t_b^\prime\};$ \\
  $\mathbf{C}.$add($P_c$); \\
  }
  \Return{$\mathbf{C}$};
  \caption{traceCurve()}
\end{algorithm}

@@

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves, $Q:$ input point}
  \KwResult{$\{t_a,t_b\}$: projections, $\{P_c, r\}$: sphere center/radius}
  $P_c \leftarrow Q$; \\
  \While{$i\texttt{++} < \;$MAX\_ITERS } {
    $\{P_A, \vec{T}_A, r_A, t_A\} \leftarrow $closestPoint$(\mathbf{A}, P_c)$;  \\
    $\{P_B, \vec{T}_B, r_B, t_B\} \leftarrow $closestPoint$(\mathbf{B}, P_c)$;  \\
    $error \leftarrow |P_A - P_c| - |P_B - P_c|;$\\ 
    \lIf{$error < \epsilon$} \textbf{break;} \\
    $P_c \leftarrow P_c - error \;\vec{n}(\vec{T}_A - \vec{T}_B);$ \\
    $\{d_A, \vec{V}_A\} \leftarrow $planeDist($P_c, P_A, P_B, \mathbf{A}.\tau(t_A + \epsilon))$;\\
    $\{d_B, \vec{V}_B\} \leftarrow $planeDist($P_c, P_B, P_A, \mathbf{B}.\tau(t_B + \epsilon))$;\\
    $P_c \leftarrow P_c - \text{PLANE\_PROJ\_COEFF} \;(d_A \vec{V}_A + d_B \vec{V}_B); $\\
  }
  \Return{$\{c_A.t, c_B.t, P_c, c_A.r\}$};
  \caption{snap()}
\end{algorithm}

@@

The effect of the average distance sampling in comparison to the original average curve
$C$ can be observed in Figure 3 between items (a) and (b). As expected, the samples
along the geodesic curve is much more refined and can sample more thoroughly the ``incompatible''
regions.

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves, $N:$ number of points}
  \KwResult{$\mathbf{G}$: geodesic average curve}
  $\mathbf{C} \leftarrow$ trace($\mathbf{A}, \mathbf{B}$); \\
  $length \leftarrow \mathbf{A}.$arcLength()$ + \mathbf{B}.$arcLength(); \\
  $\{\delta l, i, \mathbf{G}\} \leftarrow \{length / N, 0, \{\mathbf{C}[0]\}\}$;\\
  \While{true} {
    $\{g, \underline{i}, \underline{d}, \overline{i}, \overline{d}\} \leftarrow \{\mathbf{G}$.last, $i,0,-1,0\};$ \\
    \While{$i < \mathbf{C}.$length} {
      $d_A \leftarrow \mathbf{A}.$arcLength($proj(g,\mathbf{A}$), $proj(C[i], \mathbf{A}$)); \\
      $d_B \leftarrow \mathbf{B}.$arcLength($proj(g,\mathbf{B}$), $proj(C[i], \mathbf{B}$)); \\
      \lIf{$d_A + d_B < \delta l$} $\{\underline{i}, \underline{d}\} \leftarrow \{i, d_A + d_B\}$; \\
      \Else {
	$\{\underline{i}, \underline{d}\} \leftarrow \{i, d_A + d_B\};$ \\
	\textbf{break};
      }
    }
    \lIf{$i \geq \mathbf{C}.$length} break; \\
    $P_c \leftarrow $LERP$(\mathbf{C}[\underline{i}], \mathbf{C}[\overline{i}], (\delta l - \underline{d}) / (\overline{d} - \underline{d}))$;\\
    $\mathbf{G}$.add(snap($\mathbf{A}, \mathbf{B}, P_c$)); \\
  }
  \Return{$\mathbf{G}$};
  \caption{geodesicTrace()}
\end{algorithm}

@@

\newpage
\section{Visualization and Editing}\label{chapter:Visual}

\begin{figure*} %This just must appear at the page before the chapter "Displaying the average curve"
	\centering
		\begin{tabular}{cccc}
			\includegraphics[scale=0.4]{images/NoGeodesicSampling.png} & \includegraphics[scale=0.4]{images/GeodesicSampling.png} 
				& \includegraphics[scale=0.4]{images/ClosestProjections.png} & \includegraphics[scale=0.4]{images/CircularArcNet.png} \\
			\small
			a) no geodesic sampling & b) with geodesic sampling & c) the closest projections & d) net of circular arcs
		\end{tabular}
	\caption{Geodesic sampling, closest projections and circular arcs}
	\label{fig:GeodesicSampling}
\end{figure*}

We provide a framework for editing the control curve and visualizing the curve average.
More specific, we support the following features: 
\begin{itemize}
	\item Moving the control points of the two input curve
	\item Displaying the curve average with or without geodesic sampling
	\item Displaying the closest projections
	\item Displaying the circular arc and animating the curve average along it
	\item Showing the inflation tube, the envelope of the smallest spheres
\end{itemize}
We now describe the single features in more detail

@@

\subsection{Circular arc}
Instead of displaying the closest projections as straight lines, we could also draw them using circular arcs.
\begin{figure}[ht!] 
  \centering
	\begin{tikzpicture}[scale=0.5]
		\coordinate[label=right:P] (P) at (0,0);
		\coordinate[label=left:A] (A) at (-6,-2);
		\coordinate[label=right:B] (B) at (6,-2);
		\coordinate[label=right:C] (C) at (0,-20);
		\draw (P)--(A); %closest projections
		\draw (P)--(B);
		\draw[blue,thick] (6.4,-0.8) coordinate -- (5.6,-3.2) coordinate; %parts of the control curve
		\draw[green,thick] (-6.4,-0.8) coordinate -- (-5.6,-3.2) coordinate;
		\draw (-6.2,-1.4) coordinate -- (-5.6,-1.2) coordinate -- (-5.2,-2.4) coordinate -- (-5.8,-2.6) coordinate; % right angles
		\draw (6.2,-1.4) coordinate -- (5.6,-1.2) coordinate -- (5.2,-2.4) coordinate -- (5.8,-2.6) coordinate;
		\path[blue,thick] (6.4,-0.8) coordinate edge[out=70,in=-120] (6.8,1) coordinate; % control curve
		\path[blue,thick] (5.6,-3.2) coordinate edge[out=250,in=100] (5.8,-5) coordinate;
		\path[green,thick] (-6.4,-0.8) coordinate edge[out=110,in=-120] (-7,1) coordinate;
		\path[green,thick] (-5.6,-3.2) coordinate edge[out=290,in=80] (-5,-5) coordinate;
		\path[black,thick] (0,0) coordinate edge[out=90,in=-70] (-0.2,1) coordinate; % average curve
		\path[black,thick] (0,0) coordinate edge[out=-90,in=110] (0.2,-3) coordinate;
		\draw (A)--(C); %circle sides
		\draw (B)--(C);
		\coordinate[label=left:r] (r) at (-4,-8);
		\draw[red,thick] ([shift=(71.567:19)] 0,-20) arc (71.567:108.435:19); %circular arc
		\tikzset{mypoints/.style={fill=white,draw=black,thick}} %coordinate points
		\fill[mypoints] (P) circle (5.0pt);
		\fill[mypoints] (A) circle (5.0pt);
		\fill[mypoints] (B) circle (5.0pt);
		\fill[mypoints] (C) circle (5.0pt);
	\end{tikzpicture}
	\caption{circular arc}
	\label{fig:CircularArc}
\end{figure}
In Fig.\ref{fig:CircularArc}, you can see parts of the two input curves in green and blue and the curve average in black in the middle. The current trace point is $P$ and the closest projections of $P$ on the control points are $A$ and $B$. \\
We can now construct a unique circle in 3d with center $C$ and radius $r$ that goes through $A$ and $B$, the tangents at these points are $AP$ and $BP$ and lies in the convex hull of $A$,$B$ and $P$.

@@

The first way one might think of drawing it, is to circles around the average curve samples $P_i$ in the plane orthogonal to the tangents $T_i$ with radii $r_i$ and connect them to tubes. However, this approach will lead to wrong results since the closest projections to the control curves are not orthogonal to the average curve tangent. Therefore, the distance from the closest projections to the average curve is not equal to the radius of the circle when it should touch the control curves.\\

@@

\begin{figure}[ht!] 
  \centering
	\begin{tikzpicture}[scale=0.5]
		\draw[black,thick] (0,0) coordinate -- (0,10) coordinate; %curves
		\draw[green,thick] (-3,0) coordinate -- (-6,10) coordinate;
		\draw[blue,thick] (3,0) coordinate -- (6,10) coordinate;
		\coordinate[label=right:$P_{i+1}$] (P2) at (0,8) coordinate; %samples
		\coordinate[label=right:$P_{i}$] (P1) at (0,6) coordinate;
		\coordinate[label=right:$P_{i-1}$] (P0) at (0,4) coordinate;
		\draw[dashed] (0,8) coordinate -- (5,6.5) coordinate; %closest projections
		\draw[dashed] (0,8) coordinate -- (-2.5,7.25) coordinate node[below] {$r_{i+1}$} -- (-5,6.5) coordinate;
		\draw[dashed] (0,6) coordinate -- (4.5,4.65) coordinate;
		\draw[dashed] (0,6) coordinate -- (-2.25,5.325) coordinate node[below] {$r_{i}$} -- (-4.5,4.65) coordinate;
		\draw[dashed] (0,4) coordinate -- (4,2.8) coordinate;
		\draw[dashed] (0,4) coordinate -- (-2,3.4) coordinate node[below] {$r_{i-1}$} -- (-4,2.8) coordinate;
		\coordinate[label=left:$A_{i+1}$] (A2) at (-5,6.5) coordinate; %closest projection points
		\coordinate[label=left:$A_{i}$] (A1) at (-4.45,4.65) coordinate;
		\coordinate[label=left:$A_{i-1}$] (A0) at (-3.9,2.8) coordinate;
		\coordinate[label=left:$B_{i+1}$] (B2) at (5,6.5) coordinate;
		\coordinate[label=left:$B_{i}$] (B1) at (4.45,4.65) coordinate;
		\coordinate[label=left:$B_{i-1}$] (B0) at (3.9,2.8) coordinate;
		\draw[red,thick] ([shift=(180:5)] 0,6.5) arc (180:0:5 and 3); %tube elipses
		\draw[red,dashed,thick] ([shift=(180:5)] 0,6.5) arc (180:360:5 and 3);
		\draw[red,thick] ([shift=(180:4.5)] 0,4.65) arc (180:0:4.5 and 2.7);
		\draw[red,dashed,thick] ([shift=(180:4.5)] 0,4.65) arc (180:360:4.5 and 2.7);
		\draw[red,thick] ([shift=(180:3.9)] 0,2.8) arc (180:0:3.9 and 2.4);
		\draw[red,dashed,thick] ([shift=(180:3.9)] 0,2.8) arc (180:360:3.9 and 2.4);
		\tikzset{mypoints/.style={fill=white,draw=black,thick}} %coordinate points
		\foreach \p in {P0,P1,P2,A0,A1,A2,B0,B1,B2}
			\fill[mypoints] (\p) circle (5.0pt);
	\end{tikzpicture}
	\caption{inflation tube}
	\label{fig:InflationDrawing}
\end{figure}

@@

% EXAMPLES
\begin{figure*}
	\centering
		\includegraphics[scale=0.4]{images/Result1.png}
		\includegraphics[scale=0.4]{images/Result2.png}
	\caption{Example 1: a bow}
	\label{fig:Result1}
\end{figure*}
\begin{figure*}
	\centering
		\includegraphics[scale=0.4]{images/Result3.png}
	\caption{Example 2: a waterslide}
	\label{fig:Result3}
\end{figure*}

>>>>

\section{Objective}
Formally, for two curves $A$ and $B$ $\subset\mathbb{R}^3$ 
the goal is to find a curve $C$ such that for each point $c \in C$, and its closest projections
\begin{align}
a^c &= \operatornamewithlimits{argmin}\limits_{a \in A} ||a-c|| \text{, and} \\
b^c &= \operatornamewithlimits{argmin}\limits_{b \in B} ||b-c||
\end{align}

@@

\section{Input}
For simplicity, we only focus on a special case that each control curve is defined by six control points $A_0$ to $A_5$ and $B_0$ to $B_5$, such that the first and the last control points are the same.
We then interpolate between these control points to obtain the continuous curves $A$ and $B$.

@@

Once all the roots of the perpendicularity constraint are found, the ones with imaginary coefficients
and the ones with real values that are out of the [0,1] bound need to be eliminated. Moreover, to
choose the closest perpendicular point, an iterative comparison has to be executed as shown in 
Algorithm 1 for a quintic function. Note that the coefficients for the polynomial are obtained
through Matlab's symbolic toolbox.

\SetArgSty{textup}
\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{P_0, T_0, P_1, T_1\}$: control points, $Q$: input point}
  \KwResult{$t$: time in $[0,1]$ for the closest point}
  $[a,b,c,d,e,f] \leftarrow $generateDistanceCoeffs$(P_0,T_0,P_1,T_1,Q)$; \\
  $res \leftarrow $solveQuintic($a,b,c,d,e,f$); \\
  $\{minDist, t^*\} \leftarrow \{\infty,-1\}$;\\
  \ForEach{$r \in res$} {
    \lIf{$|r.im| > 0$} {
			\textbf{continue}
		}
    \lIf{$r.re < 0\;$ \textbf{or} $\;r.re > 1$} {
			\textbf{continue}
		}
    $P_t \leftarrow \tau(P_0,T_0,P_1,T_1,r.re)$; \\
    \If{$|P_t - Q| < minDist$} {
      $\{minDist, t^*\} \leftarrow \{|P_t - Q|, r.re\}$;\\
    }
  }
  \Return{$t^*$};
  \caption{closestPointOnCubicHermite()}
\end{algorithm}

@@

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves}
  \KwResult{$\mathbf{C}$: average curve}
  $\mathbf{C}.$add($\mathbf{A}[0], 0$); \\
  $\{current, t_a, t_b, t_a^\prime, t_b^\prime\} \leftarrow \{\mathbf{C}[0],0,0,0,0\}$; \\
  \While{true} {
  $\vec{T}_A \leftarrow \vec{n}$($\mathbf{A}.\tau$($min(1,t_a+\epsilon)$) - $\mathbf{A}.\tau$($min(1,t_a)$)); \\
  $\vec{T}_B \leftarrow \vec{n}$($\mathbf{B}.\tau$($min(1,t_b+\epsilon)$) - $\mathbf{B}.\tau$($min(1,t_b)$)); \\
  $current \stackrel{+}\leftarrow \text{STEP\_SIZE} \;\vec{n}(\vec{T}_A + \vec{T}_B)$; \\
  $\{t_a^\prime, t_b^\prime, r, P_c\} \leftarrow \text{snap}(\mathbf{A},\mathbf{B},current)$; \\
  \lIf{$max(t_a,t_b) < 1$ \textbf{or} $t_a^\prime < t_a$ \textbf{or} $t_b^\prime < t_b$} {
		\textbf{  break}
	}
  $\{t_a, t_b\} \leftarrow \{t_a^\prime, t_b^\prime\};$ \\
  $\mathbf{C}.$add($P_c$); \\
  }
  \Return{$\mathbf{C}$};
  \caption{traceCurve()}
\end{algorithm}

@@

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves, $Q:$ input point}
  \KwResult{$\{t_a,t_b\}$: projections, $\{P_c, r\}$: sphere center/radius}
  $P_c \leftarrow Q$; \\
  \While{$i\texttt{++} < \;$MAX\_ITERS } {
    $\{P_A, \vec{T}_A, r_A, t_A\} \leftarrow $closestPoint$(\mathbf{A}, P_c)$;  \\
    $\{P_B, \vec{T}_B, r_B, t_B\} \leftarrow $closestPoint$(\mathbf{B}, P_c)$;  \\
    $error \leftarrow |P_A - P_c| - |P_B - P_c|;$\\ 
    \lIf{$error < \epsilon$} {\textbf{break}}
    $P_c \leftarrow P_c - error \;\vec{n}(\vec{T}_A - \vec{T}_B);$ \\
    $\{d_A, \vec{V}_A\} \leftarrow $planeDist($P_c, P_A, P_B, \mathbf{A}.\tau(t_A + \epsilon))$;\\
    $\{d_B, \vec{V}_B\} \leftarrow $planeDist($P_c, P_B, P_A, \mathbf{B}.\tau(t_B + \epsilon))$;\\
    $P_c \leftarrow P_c - \text{PLANE\_PROJ\_COEFF} \;(d_A \vec{V}_A + d_B \vec{V}_B); $\\
  }
  \Return{$\{c_A.t, c_B.t, P_c, c_A.r\}$};
  \caption{snap()}
\end{algorithm}

@@

The effect of the average distance sampling in comparison to the original average curve
$C$ can be observed in Fig.\ref{fig:GeodesicSampling} between items (a) and (b). As expected, the samples
along the geodesic curve is much more refined and can sample more thoroughly the ``incompatible''
regions.

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$\{\mathbf{A},\mathbf{B}\}$: curves, $N:$ number of points}
  \KwResult{$\mathbf{G}$: geodesic average curve}
  $\mathbf{C} \leftarrow$ trace($\mathbf{A}, \mathbf{B}$); \\
  $length \leftarrow \mathbf{A}.$arcLength()$ + \mathbf{B}.$arcLength(); \\
  $\{\delta l, i, \mathbf{G}\} \leftarrow \{length / N, 0, \{\mathbf{C}[0]\}\}$;\\
  \While{true} {
    $\{g, \underline{i}, \underline{d}, \overline{i}, \overline{d}\} \leftarrow \{\mathbf{G}$.last, $i,0,-1,0\};$ \\
    \While{$i < \mathbf{C}.$length} {
      $d_A \leftarrow \mathbf{A}.$arcLength($proj(g,\mathbf{A}), proj(C[i], \mathbf{A})$); \\
      $d_B \leftarrow \mathbf{B}.$arcLength($proj(g,\mathbf{B}), proj(C[i], \mathbf{B})$); \\
      \lIf{$d_A + d_B < \delta l$} $\{\underline{i}, \underline{d}\} \leftarrow \{i, d_A + d_B\}$; \\
      \Else {
	$\{\underline{i}, \underline{d}\} \leftarrow \{i, d_A + d_B\};$ \\
	\textbf{break};
      }
    }
    \lIf{$i \geq \mathbf{C}.$length} {
			\textbf{break}
		}
    $P_c \leftarrow $LERP$(\mathbf{C}[\underline{i}], \mathbf{C}[\overline{i}], (\delta l - \underline{d}) / (\overline{d} - \underline{d}))$;\\
    $\mathbf{G}$.add(snap($\mathbf{A}, \mathbf{B}, P_c$)); \\
  }
  \Return{$\mathbf{G}$};
  \caption{geodesicTrace()}
\end{algorithm}

@@

\begin{figure*} %This just must appear at the page before the chapter "Displaying the average curve"
	\centering
		\begin{tabular}{cccc}
			\includegraphics[scale=0.4]{images/NoGeodesicSampling.png} & \includegraphics[scale=0.4]{images/GeodesicSampling.png} 
				& \includegraphics[scale=0.4]{images/ClosestProjections.png} & \includegraphics[scale=0.4]{images/CircularArcNet.png} \\
			\small a) no geodesic sampling & \small b) with geodesic sampling 
			  & \small c) the closest projections & \small d) net of circular arcs
		\end{tabular}
	\caption{Geodesic sampling, closest projections and circular arcs}
	\label{fig:GeodesicSampling}
\end{figure*}

\section{Visualization and Editing}\label{chapter:Visual}

We provide a framework for editing the control curve and visualizing the curve average.
More specific, we support the following features: 
\begin{itemize}
	\item Moving the control points of the two input curve
	\item Displaying the curve average with or without geodesic sampling
	\item Displaying the closest projections
	\item Displaying the circular arc and animating the curve average along it
	\item Showing the inflation tube, the envelope of the smallest spheres
\end{itemize}
We now describe the single features in more detail.

@@

\subsection{Circular arc}
Instead of displaying the closest projections as straight lines, we could also draw them using circular arcs.
\begin{figure}[ht!] 
  \centering
	\begin{tikzpicture}[scale=0.5]
		\coordinate[label=right:P] (P) at (0,0);
		\coordinate[label=left:A] (A) at (-6,-2);
		\coordinate[label=right:B] (B) at (6,-2);
		\coordinate[label=right:C] (C) at (0,-20);
		\draw (P)--(A); %closest projections
		\draw (P)--(B);
		\draw[blue,thick] (6.4,-0.8) coordinate -- (5.6,-3.2) coordinate; %parts of the control curve
		\draw[green,thick] (-6.4,-0.8) coordinate -- (-5.6,-3.2) coordinate;
		\draw (-6.2,-1.4) coordinate -- (-5.6,-1.2) coordinate -- (-5.2,-2.4) coordinate -- (-5.8,-2.6) coordinate; % right angles
		\draw (6.2,-1.4) coordinate -- (5.6,-1.2) coordinate -- (5.2,-2.4) coordinate -- (5.8,-2.6) coordinate;
		\path[blue,thick] (6.4,-0.8) coordinate edge[out=70,in=-120] (6.8,1) coordinate; % control curve
		\path[blue,thick] (5.6,-3.2) coordinate edge[out=250,in=100] (5.8,-5) coordinate;
		\path[green,thick] (-6.4,-0.8) coordinate edge[out=110,in=-120] (-7,1) coordinate;
		\path[green,thick] (-5.6,-3.2) coordinate edge[out=290,in=80] (-5,-5) coordinate;
		\path[black,thick] (0,0) coordinate edge[out=90,in=-70] (-0.2,1) coordinate; % average curve
		\path[black,thick] (0,0) coordinate edge[out=-90,in=110] (0.2,-3) coordinate;
		\draw (A)--(C); %circle sides
		\draw (B)--(C);
		\coordinate[label=left:r] (r) at (-4,-8);
		\draw[red,thick] ([shift=(71.567:19)] 0,-20) arc (71.567:108.435:19); %circular arc
		\tikzset{mypoints/.style={fill=white,draw=black,thick}} %coordinate points
		\fill[mypoints] (P) circle (5.0pt);
		\fill[mypoints] (A) circle (5.0pt);
		\fill[mypoints] (B) circle (5.0pt);
		\fill[mypoints] (C) circle (5.0pt);
	\end{tikzpicture}
	\caption{circular arc}
	\label{fig:CircularArc}
\end{figure}
In Fig.\ref{fig:CircularArc}, you can see parts of the two input curves in green and blue and the curve average in black in the middle. The current trace point is $P$ and the closest projections of $P$ on the control points are $A$ and $B$. \\
We can now construct a unique circle in $\mathbb{R}^3$ with center $C$ and radius $r$ that goes through $A$ and $B$, the tangents at these points are $AP$ and $BP$ and lies in the convex hull of $A$,$B$ and $P$.

@@

The first way one might think of drawing it, is to circles around the average curve samples $P_i$ in the plane orthogonal to the tangents $T_i$ with radii $r_i$ and connect them to tubes. However, this approach will lead to wrong results since the closest projections to the control curves are not orthogonal to the average curve tangent. Therefore, the distance from the closest projections to the average curve is not equal to the radius of the circle when it should touch the control curves.

@@

\begin{figure}[ht!] 
  \centering
	\begin{tikzpicture}[scale=0.6]
		\draw[black,thick] (0,0) coordinate -- (0,10) coordinate; %curves
		\draw[green,thick] (-3,0) coordinate -- (-6,10) coordinate;
		\draw[blue,thick] (3,0) coordinate -- (6,10) coordinate;
		\coordinate[label=right:$P_{i+1}$] (P2) at (0,8) coordinate; %samples
		\coordinate[label=right:$P_{i}$] (P1) at (0,6) coordinate;
		\coordinate[label=right:$P_{i-1}$] (P0) at (0,4) coordinate;
		\draw[dashed] (0,8) coordinate -- (5,6.5) coordinate; %closest projections
		\draw[dashed] (0,8) coordinate -- (-2.5,7.25) coordinate node[below] {$r_{i+1}$} -- (-5,6.5) coordinate;
		\draw[dashed] (0,6) coordinate -- (4.5,4.65) coordinate;
		\draw[dashed] (0,6) coordinate -- (-2.25,5.325) coordinate node[below] {$r_{i}$} -- (-4.5,4.65) coordinate;
		\draw[dashed] (0,4) coordinate -- (4,2.8) coordinate;
		\draw[dashed] (0,4) coordinate -- (-2,3.4) coordinate node[below] {$r_{i-1}$} -- (-4,2.8) coordinate;
		\coordinate[label=left:$A_{i+1}$] (A2) at (-5,6.5) coordinate; %closest projection points
		\coordinate[label=left:$A_{i}$] (A1) at (-4.45,4.65) coordinate;
		\coordinate[label=left:$A_{i-1}$] (A0) at (-3.9,2.8) coordinate;
		\coordinate[label=left:$B_{i+1}$] (B2) at (5,6.5) coordinate;
		\coordinate[label=left:$B_{i}$] (B1) at (4.45,4.65) coordinate;
		\coordinate[label=left:$B_{i-1}$] (B0) at (3.9,2.8) coordinate;
		\draw[red,thick] ([shift=(180:5)] 0,6.5) arc (180:0:5 and 3); %tube elipses
		\draw[red,dashed,thick] ([shift=(180:5)] 0,6.5) arc (180:360:5 and 3);
		\draw[red,thick] ([shift=(180:4.5)] 0,4.65) arc (180:0:4.5 and 2.7);
		\draw[red,dashed,thick] ([shift=(180:4.5)] 0,4.65) arc (180:360:4.5 and 2.7);
		\draw[red,thick] ([shift=(180:3.9)] 0,2.8) arc (180:0:3.9 and 2.4);
		\draw[red,dashed,thick] ([shift=(180:3.9)] 0,2.8) arc (180:360:3.9 and 2.4);
		\tikzset{mypoints/.style={fill=white,draw=black,thick}} %coordinate points
		\foreach \p in {P0,P1,P2,A0,A1,A2,B0,B1,B2}
			\fill[mypoints] (\p) circle (5.0pt);
	\end{tikzpicture}
	\caption{inflation tube}
	\label{fig:InflationDrawing}
\end{figure}

@@

% EXAMPLES
\begin{figure*}
	\centering
		\includegraphics[scale=0.5]{images/Result1.png}
		\includegraphics[scale=0.5]{images/Result2.png}
	\caption{Example 1: a bow}
	\label{fig:Result1}
\end{figure*}
\begin{figure*}
	\centering
		\includegraphics[scale=0.6]{images/Result3.png}
	\caption{Example 2: a waterslide}
	\label{fig:Result3}
\end{figure*}
